### 2017-06-21 src/algorithm.tex
fix

In this section we present an FPTAS algorithm to the \VPN{} problem.
We are given an instance of the \VPN{} problem 
\begin{align*}
D_v = (\beta , A_v)		\\
D_p = (v, A_p)		\\
(\sigma , \tau , s, t)	\\
(p_d, b_d, p_c, b_c, c)
\end{align*}
For now, assume all values are integral and polynomial bounded in the size of
the input.
Under this assumption we show that an optimal embedding can be computed
efficiently.
We then argue that, using a standard scaling and rounding technique, we can use
the same computation to achieve a solution with a cost only
$1 + \varepsilon$ times greater that of the optimal solution, for any
$\varepsilon > 0$.
Also, for convenient and w.l.o.g, assume that $\sigma , \tau $ are dummy vertices, 
i.e. $c(\sigma , v) = c(\tau , v) = 0$ for every $v \in v$.

We start by arguing that the minimum processing time required to embed some
$\alpha \gamma $-path into a vertex $v$ can be computed efficiently.
Let $P_{v}(\alpha , \gamma , C)$ denote the minimum processing required to embed
all the virtual vertices, excluding $\alpha $, on a $\alpha \gamma $-path into the physical
vertex $v$ with cost constraint $C$.
$P$ can be computed recursively as follow:
\begin{align*}
&P_{v}(\alpha , \gamma , C) = 
\min_{\alpha \beta  \in A_v} P_{v}(\alpha , \beta , C - c(\gamma , v))
\\
&P(\alpha , \alpha , C) = 0
\\
&P(-, -, <0) = \infty
\end{align*}

We now show how to compute the optimal embedding.
Let $C(\gamma , w)$ denote the
optimal embedding of a $\sigma \gamma $-path into a $sw$-path.
Let $\pi:\beta  \to \N$ be any typological ordering of $\beta $. 
We claim that $O$ can be computed recursively as follow:
\begin{align*}
&C(\gamma , w) = 
\min_{\substack{
\alpha  : pi(\alpha ) \leq pi(\beta ), 
\\
vw \in A_p
}}
C(\alpha , u)
+
\argmin_{C : P_{w}(\beta , \gamma , C) \leq p_c(w)}
\\
&C(\sigma , w) = c(\sigma , w)
\end{align*}
Now, to compute the optimal embedding, one need to compute $C(\tau , t)$. 
We also note that in order to obey to the bandwidth constraints, 
one need to temporally remove all edges $\alpha \beta $ with bandwidth greater than
$b_c(v, w)$ from the virtual graph and only then compute $P_{w}(\beta , \gamma , C)$.
The above formulation is illustrated in Figure~\ref{fig:dp1}.

\begin{figure}[ht]
\centering
\input{fig-dp2}
\caption[]{
\label{fig:dp1}
The optimal embedding of a $\sigma \gamma $-path into a $sv$ path can be
efficiently computed by breaking the problem into the problem of embedding 
a $\sigma \alpha $-path into a $su$-path (blue, dashed clouds) 
and the problem of embedding a $\beta \gamma $-path into $v$ (orange, dotted) 
where $b_d(\alpha , \beta) \leq b_c(u, v)$.
}
\end{figure}

>>>>

In this section, 
assuming costs are integral and polynomial bounded in the input length,
we present an efficient algorithm to the \VPN{} problem.
We then argue that, using a standard scaling and rounding technique, we can use
the same computation to achieve a solution with a cost only
$1 + \varepsilon$ times greater that of the optimal solution, for any
$\varepsilon > 0$, i.e. an FPTAS also for an arbitrary cost function.
We also extend our algorithm when every physical arc carry some latency on it
and a global latency constraint is given.

We are given an instance of the \VPN{} problem 
\begin{align*}
D_v = (\beta , A_v)		\\
D_p = (v, A_p)		\\
(\sigma , \tau , s, t)	\\
(p_d, b_d, p_c, b_c, c)
\end{align*}
Also, for convenient and w.l.o.g, assume that $\sigma , \tau $ are dummy vertices, 
i.e. $c(\sigma , v) = c(\tau , v) = 0$ for every $v \in V_p$ and that
$b_d(\sigma\alpha) = b_d(\alpha\tau) = 0$ for every $\alpha \in V_v$.

We start by arguing that the minimum processing time required to embed some
$\alpha \gamma $-path into a vertex $v$ given a cost constraint can be computed
efficiently.
Let $P_{v}(\alpha , \gamma , C)$ denote the minimum processing required to embed
all the virtual vertices, excluding $\alpha $, on a $\alpha \gamma $-path into the physical
vertex $v$ with a cost constraint $C$.
$P$ can be computed recursively as follow:
\begin{align*}
&P_{v}(\alpha , \gamma , C) = 
\min_{\alpha \beta  \in A_v} P_{v}(\alpha , \beta , C - c(\gamma , v))
\\
&P(\alpha , \alpha , C) = 0
\\
&P(-, -, <0) = \infty
\end{align*}

We now show how to compute the optimal embedding.
Let $C(\gamma , w)$ denote the
optimal embedding of a $\sigma \gamma $-path into a $sw$-path.
Let $\pi:\beta  \to \N$ be any typological ordering of $\beta $. 
We claim that $C$ can be computed recursively as follow:
\begin{align*}
&C(\gamma , w) = 
\min_{\substack{
\alpha  : \pi(\alpha ) \leq \pi(\beta ), 
\\
vw \in A_p
}}
C(\alpha , u)
+
\argmin_{C : P_{w}(\beta , \gamma , C) \leq p_c(w)}
\\
&C(\sigma , w) = c(\sigma , w)
\end{align*}
Now, to compute the optimal embedding, one need to compute $C(\tau , t)$. 
We also note that in order to obey to the bandwidth constraints, 
one need to temporally remove all edges $\alpha \beta $ with bandwidth greater than
$b_c(v, w)$ from the virtual graph and only then compute $P_{w}(\beta , \gamma , C)$.
The above formulation is illustrated in Figure~\ref{fig:dp1}.

\begin{figure}[h]
\centering
\input{fig-dp2}
\caption[]{
\label{fig:dp1}
The optimal embedding of a $\sigma \gamma $-path into a $sv$ path can be
efficiently computed by breaking the problem into the problem of embedding 
a $\sigma \alpha $-path into a $su$-path (blue, dashed clouds) 
and the problem of embedding a $\beta \gamma $-path into $v$ (orange, dotted) 
where $b_d(\alpha , \beta) \leq b_c(u, v)$.
Virtual arcs with high bandwidth demand (dashed arc) need to be removed before
the computation of the optimal path embedding.
}
\end{figure}
